From Education to Entrepreneurship

### 2014-12-11 index.Rmd
Edited code block
Editing output from charts

```{r echo = FALSE, cache= FALSE, include= TRUE}

@@

# Create plot of WoT and PercentOwner
CD_subset %>% 
  ggvis(~WayofTeaching, ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")
```

@@

# Create plot of PercentOpp and PercentOwner
CD_subset2 %>% 
  ggvis(~PercentOpportunities, ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")

>>>>

```{r echo = FALSE, cache= FALSE, include= TRUE, results='asis', warning=FALSE}

@@

# Create plot of WoT and PercentOwner
CD_subset %>% 
  ggvis(x = ~WayofTeaching, y = ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")
```

@@

# Create plot of PercentOpp and PercentOwner
CD_subset2 %>% 
  ggvis(x = ~PercentOpportunities, y = ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")
